### 2021-09-13 presentation/presentation.tex
remove useless slide
notes and webcast options
update sizes
script for presentation

\documentclass[aspectratio=169]{beamer}
% \includeonlyframes{current}

\mode<presentation>
{
  \usetheme{Luebeck}
  % \usetheme{Madrid}
  % \usetheme{Warsaw}
  % \usetheme{Copenhagen}
  % \usecolortheme{beaver}
  % \usecolortheme{rose}
  % or ...
  % \usecolortheme{beaver}
  \useoutertheme{split}
  \useinnertheme{circles}
  \usefonttheme[onlymath]{serif}
\definecolor{supelecRed}{RGB}{120,30,56}
\definecolor{supelecPurple}{RGB}{104,95,115}
%
  % \setbeamercolor{palette primary}{bg=red!50!black!80}
  \setbeamercolor{palette primary}{bg=supelecRed}
  % \setbeamercolor{palette secondary}{bg=red!50!black!70}
  \setbeamercolor{palette secondary}{bg=supelecRed}
  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
  % \setbeamercolor{palette tertiary}{bg=supelecPurple}
  \setbeamercolor{palette quaternary}{bg=gray!90!black!90}
  % \setbeamercolor{palette quaternary}{bg=supelecPurple}
  % \setbeamercolor{block title}{bg=red!50!black!70}
  \setbeamercolor{block title}{bg=supelecRed}
  \setbeamercolor{block title example}{bg=gray!90!black!90}
  \setbeamercolor{block title example}{bg=gray!90!black!90}

@@

  % \setbeamercolor{author in head/foot}{bg=grey!60}
  \setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
\makeatletter
\protected\def\protectedempty{}
\setbeamertemplate{page number in head/foot}[appendixframenumber]
\setbeamertemplate{footline}
{%
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
    \centering
    \usebeamerfont{date in head/foot}\usebeamercolor[fg]{page number in head/foot}\usebeamerfont{page number in head/foot}\usebeamertemplate{page number in head/foot}
    % \hspace*{2ex}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \centering
    \usebeamerfont{author in head/foot}\insertshortauthor{}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.65\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
    \centering
    \insertshorttitle{}
  \end{beamercolorbox}%
  }%
  \vskip0pt%
}
\makeatother

\setbeamertemplate{sidebar right}{
  \vfill%
  \llap{\insertlogo\hskip0.2cm}%
  \vskip3pt%
  \llap{\usebeamertemplate***{navigation symbols}\hskip0.1cm}%
  \vskip2pt%
}
\setbeamertemplate{headline}
{%
  \leavevmode%
  \hbox{%
      \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{section in head/foot}%
      \centering
      \usebeamerfont{author in head/foot}\insertsection{}
    \end{beamercolorbox}%
  % }
    \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{subsection in head/foot}%
      \centering
      \insertsubsection{}
    \end{beamercolorbox}%
    }
  \vskip0pt%
}

@@

\logo{\includegraphics[height=.8cm]{logos/supelec.jpeg}}

@@

\begin{frame}[plain]
  \titlepage%
\end{frame}

@@

\begin{frame}{Context}
  \centering
  Smart City\\
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
  \end{minipage}
  \only<2-5>{
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<2> Energy Distribution System
      \item<3> Traffic management
      \item<4> Heat distribution
      \item<5> Water distribution
      \item<5>[] \dots
    \end{itemize}
  \end{minipage}
  }
\only<6->{
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<6> Geographically distributed
      \item<7> Coupled by constraints (energy)
      \item<8> Optimization objectives
            \begin{itemize}
              \item Energy
              \item User satisfaction
              \item \dots
            \end{itemize}
      \item<9> Solution $\to$ Model Predictive Control
    \end{itemize}
  \end{minipage}
  }
\end{frame}

\begin{frame}{Model Predictive Control}
  Objective: Find control input sequence that optimizes an objective function
  \only<1-5>{\begin{equation*}
    \begin{matrix}
      \underset{\vec{u}(k:k+\alert<3>{N_{p}}-1|k)}{\mathrm{optimize}}&\alert<2>{J(\vec{x}(k),\vec{u}(k))}\\
      \mathrm{subject~ to}&
      \left.
        \begin{matrix}
          \alert<4>{\vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi))}\\
          \alert<5>{g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0}\\
          \alert<5>{h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0}\\
        \end{matrix}
      \right\}
      \begin{aligned}
        &\forall \xi\in\{1,\dots,\alert<3>{N_{p}}\}\\
        &\forall i\in\{1,\dots,m\}\\
        &\forall j\in\{1,\dots,p\}
      \end{aligned}
    \end{matrix}
  \end{equation*}}%
\only<6->{
  \begin{equation*}
    \begin{matrix}
      \underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&  \sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}\\
      \mathrm{subject~ to}&
      \left.
        \begin{matrix}
          \vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi)) \\
          g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0\\
          h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0\\
        \end{matrix}
      \right\}
      \begin{aligned}
        &\forall \xi\in\{1,\dots,N_{p}\}\\
        &\forall i\in\{1,\dots,m\}\\
        &\forall j\in\{1,\dots,p\}
      \end{aligned}
    \end{matrix}
  \end{equation*}
  }%
\end{frame}

@@

\begin{frame}{Model Predictive Control}
  \only<1->{Find optimal control sequence}%
  \only<2->{, apply first element}%
  \only<3->{, rinse repeat}%
  \only<4->{ $\to$ Receding Horizon}%

  \begin{figure}
    \centering
    \foreach \i in {1,...,4}{%
      % \includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
      \only<{\i}>{\input{../img/mpcState\i.tex}}%
      \only<{\i}>{\input{../img/mpcControl\i.tex}}%
    }
  \end{figure}
\end{frame}

\begin{frame}{Distributed Model Predictive Control}
  \begin{itemize}
    \item<1> Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
    \item<2> Solution: Divide and Conquer
  \end{itemize}
  \vfill
  \centering
  \begin{minipage}[c]{.45\linewidth}
    \begin{figure}
      \centering
      \only<1>{
        \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
          \node[draw,
          rectangle,
          trapezium stretches,
          align=center,
          fill=supelecRed!10,
          alt=<{3}>{fill=supelecRed!90,text=white},
          minimum width=3.5cm,
          minimum height=4cm
          ] (block1) {MPC};
        \end{tikzpicture}
      }%
      \only<2>{
        \begin{tikzpicture}[font=\small,thick,node distance=.2cm and .5cm,
          mpcSmall/.style={
            rectangle,
            align=center,
            fill=supelecRed!10,
            minimum width=2.cm,
            minimum height=.4cm},
          coordinator/.style={
            rectangle,
            align=center,
            fill=supelecRed!10,
            minimum width=1cm,
            minimum height=4cm
          } ]

@@

        \end{tikzpicture}
      }%
    \end{figure}
  \end{minipage}
\end{frame}

\begin{frame}{Distributed Model Predictive Control}{Quantity Decomposition | Resource Allocation}
  \centering
  \only<4>{
    \begin{minipage}[t]{.3\linewidth}
      \begin{figure}[!t]
        \scalebox{.7}{\footnotesize \def\svgwidth{8cm} \input{../img/diagQuantMod.pdf_tex}}
      \end{figure}
    \end{minipage}
    \hfill
  }
  \only<1>{
    \begin{equation*}
      \scalebox{1}{
        $\displaystyle
        \begin{matrix}
          \underset{\vec{u}_i(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\overbrace{\sum\limits^{M}_{i=1} \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}_i(k+j|k)\|^{2}_{Q_i}+\|\vec{u}_i(k+j-1|k)\|^{2}_{R_i}}^{\textstyle J_{i}(k)}}^{\textstyle J_{G}(k)}\\
          \mathrm{subject~ to}&
          \left.
            \begin{matrix}
              \vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
              \sum^{M}_{i=1}\Gamma_{i}\vec{u}_{i}(k)=\vec{u}_{\mathrm{\max}}\\
            \end{matrix}
          \right\}
          \begin{aligned}
            &\forall i\in\{1,\dots,M\}\\
            &\forall j\in\{1,\dots,N_{p}\}
          \end{aligned}
        \end{matrix}
        $}
    \end{equation*}
  }
  \only<2->{
    \begin{minipage}[t]{.6\linewidth}
      \centering
      \begin{equation*}
        \scalebox{.8}{
          $\displaystyle
          \left.
            \small
            \begin{aligned}
              J_{i}^{\star}(\vec{\theta}_{i}(k))&=\underset{\vec{u}_{i}(k:k+N_{p}-1|k)}{\mathrm{minimize}}J_i(k)\\
              \mathrm{s.t.} &\quad\vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
              &\quad\Gamma_{i}\vec{u}_i(k)=\vec{\theta}_{i}(k):\vec{\lambda}_{i}(k)\\
            \end{aligned}
          \right\}
          \small
          \begin{aligned}
            &\forall i\in\{1,\dots,M\}\\
            &\forall j\in\{1,\dots,N_{p}\}
          \end{aligned}
          \label{eq:DOP_local}
          $}
      \end{equation*}
      \vfill
      \begin{equation*}
        \small
        \begin{aligned}
          \only<2>{
            J^{\star}&=\underset{\vec{\theta}(k:k+N_{p}-1|k)}{\mathrm{minimize}}\sum^{M}_{i=1} J^{\star}_i(\vec{\theta}_i(k))\\
            \mathrm{s.t.} &\quad \sum_{i=1}^{M}\vec{\theta}_{i}(k)=\vec{u}_{\max}
          }
          \only<3->{
            \vec{\theta}_{i}\pplusone=\vec{\theta}_{i}\p+\rho\left(\vec{\lambda}_{i}^{\star}(\vec{\theta}_{i}\p)-\frac{1}{M}\sum^{M}_{j=1} \vec{\lambda}_{j}^{\star}(\vec{\theta}_{j}\p)\right)
          }
        \end{aligned}
      \end{equation*}
    \end{minipage}
  }
\end{frame}
% \begin{frame}
%   \centering
%   \begin{minipage}{.65\linewidth}
%     \begin{algorithm}[H]
%       \DontPrintSemicolon
%       Coordinator initializes $\vec{\theta}^{(0)}$ \;
%       $p:=0$\;
%       \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
%         Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
%         Coordinator updates allocations~\eqref{eq:thetaNegot}\;
%         $p:=p+1$
%       }
%       \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
%     \end{algorithm}
%   \end{minipage}
% \end{frame}

\begin{frame}{Quantity Decomposition | Resource Allocation}
  \begin{figure}
    \centering
    \scalebox{.55}{
      \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
        \node[draw,
        rounded rectangle,
        fill=gray!90!black!50,
        alt=<{2}>{fill=supelecRed!90,text=white},
        minimum width=2.5cm,
        minimum height=1cm] (block1) {Start};

@@

      \end{tikzpicture}
    }
    \caption{Quantity decomposition based DMPC}\label{fig:quantityDecompDMPC}
  \end{figure}
\end{frame}

\begin{frame}{}
  \centering
  \vfill
What if agents send a non-agreed $\vec{\lambda}_{i}$?
  \vfill
\end{frame}

\begin{frame}{Outline}
  % \tableofcontents
  \tableofcontents[subsectionstyle=show/show/show]
  % You might wish to add the option [pausesections]
\end{frame}

@@

  \begin{itemize}
    \item<1-> $\vec{\lambda}_{i}$ is the only interface with coordination
    \item<2-> Non-cooperative agent sends $\tilde{\vec{\lambda}}_{i}=\gamma_{i}(\vec{\lambda}_{i})$\pause
  \end{itemize}

\subsection{Consequences}
\begin{frame}{Example}
  \begin{minipage}[c]{.45\linewidth}
    \begin{figure}[!t]
      \centering
      \begin{tikzpicture}
        \node (0,0){\includegraphics[width=\textwidth]{changeOfJ.pdf}};
        \draw<4>[rounded corners,red,thick] (-2.5,2.5) rectangle +(.5,-5);
        \draw<5>[rounded corners,red,thick] (2.5,2.5) rectangle +(.75,-5);
      \end{tikzpicture}
    \end{figure}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{.45\linewidth}
    \begin{exampleblock}{4 distinct agents}
      \begin{itemize}
        \item<2-> Agent 1 is non-cooperative\\
        \item<3-> It uses $\tilde{\vec{\lambda}}_{1}=\gamma_{1}(\vec{\lambda}_{1})=\tau_{1}I\vec{\lambda}_{1}$
      \end{itemize}
    \end{exampleblock}
  \end{minipage}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\section{Securing the DMPC}

@@

\end{itemize}
\end{frame}

@@

      \node[] at (5cm,0cm) {\Large Detection Phase};
      \node[] at (11cm,0cm) {\Large Negotiation Phase};

>>>>

\documentclass[aspectratio=169]{beamer}
% \includeonlyframes{current}
\usepackage{pgfpages}
% \setbeameroption{show notes on second screen}
\newif\ifwebcast
\webcastfalse
\newcommand{\webcast}{\webcasttrue}
% \webcast
\newcommand<>{\script}[1]{\note{\onslide#2{#1}}}

\mode<presentation>
{
  \usetheme{Luebeck}
  % \usetheme{Madrid}
  % \usetheme{Warsaw}
  % \usetheme{Copenhagen}
  % \usecolortheme{beaver}
  % \usecolortheme{rose}
  % or ...
  % \usecolortheme{beaver}
  \useoutertheme{split}
  \useinnertheme{circles}
  \usefonttheme[onlymath]{serif}

\definecolor{supelecRed}{RGB}{120,30,56}
\definecolor{supelecPurple}{RGB}{104,95,115}
%
  % \setbeamercolor{palette primary}{bg=red!50!black!80}
  \setbeamercolor{palette primary}{bg=supelecRed}
  % \setbeamercolor{palette secondary}{bg=red!50!black!70}
  \setbeamercolor{palette secondary}{bg=supelecRed}
  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
  % \setbeamercolor{palette tertiary}{bg=supelecPurple}
  \setbeamercolor{palette quaternary}{bg=gray!90!black!90}
  % \setbeamercolor{palette quaternary}{bg=supelecPurple}
  % \setbeamercolor{block title}{bg=red!50!black!70}
  \setbeamercolor{block title}{bg=supelecRed}
  \setbeamercolor{block title example}{bg=gray!90!black!90}
  \setbeamercolor{block title example}{bg=gray!90!black!90}

@@

  % \setbeamercolor{author in head/foot}{bg=grey!60}
  \setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
\makeatletter
\protected\def\protectedempty{}
\setbeamertemplate{page number in head/foot}[appendixframenumber]

\setbeamertemplate{footline}
{%
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
    \centering
    \usebeamerfont{date in head/foot}\usebeamercolor[fg]{page number in head/foot}\usebeamerfont{page number in head/foot}\usebeamertemplate{page number in head/foot}
    % \hspace*{2ex}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \centering
    \usebeamerfont{author in head/foot}\insertshortauthor{}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.65\paperwidth,ht=2.25ex,dp=1ex,right]{title in head/foot}%
    \centering
    \insertshorttitle{}
  \end{beamercolorbox}%
  }%
  \vskip0pt%
}

\setbeamertemplate{note page}{
  \vfill
\insertnote
  \vfill
}

\setbeamersize{text margin right=1.5cm}
\setbeamersize{text margin left=1.5cm}

\setbeamertemplate{sidebar right}{
  % \vskip1.3cm%
  % \llap{\tikz{\draw[fill=black] (.75,0) circle [radius=.75cm]}\hskip0.2cm}%
  \vfill%
  \llap{\insertlogo\hskip0.2cm}%
  \vskip3pt%
}
\setbeamertemplate{sidebar left}{
  \vfill%
  \ifwebcast{\hspace{3pt}\tikz{\draw[fill=pink,draw=pink] (.6,0) circle [radius=.6cm]}}%
  \else%
  % \hspace{3pt}\tikz{\draw[fill=white,draw=white] (.6,0) circle [radius=.6cm]}%
  \fi
  \vskip3pt%
}

\setbeamertemplate{headline}
{%
  \leavevmode%
  \hbox{%
      \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{section in head/foot}%
      \centering
      \usebeamerfont{author in head/foot}\insertsection{}
    \end{beamercolorbox}%
    \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,right]{subsection in head/foot}%
      \centering
      \insertsubsection{}
    \end{beamercolorbox}%
    }
  \vskip0pt%
}

@@

\logo{\includegraphics[width=1.5cm]{logos/supelec.jpeg}}

@@

\begin{frame}[plain]
  \titlepage%
  \note{15 minutes !!!!\\}
  \script{Hello, I'm Rafael Accácio and on behalf of my co Authors Romain Bourdais and Hervé Guéguen I'm here to present our paper for the SysTol'21 called «Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation».\\}
  \script{This presentation is available at the address shown or by flashing the QR code.\\}
\end{frame}

@@

\begin{frame}{Context}
  \centering
  % \only<6>{
  % Smart City\\}
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
  \end{minipage}
  \only<1-4>{
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<+> Energy Distribution System
      \item<+> Traffic management
      \item<+> Heat distribution
      \item<+> Water distribution\\\dots
    \end{itemize}
  \end{minipage}
  }
\only<5->{
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<5> Geographically distributed
      \item<6> Coupled by constraints (energy)
      \item<7> Optimization objectives
            \begin{itemize}
              \item Energy
              \item User satisfaction
              \item \dots
            \end{itemize}
      \item<8-> Solution $\to$ Model Predictive Control
    \end{itemize}
  \end{minipage}
  }
  \script<1->{With the ever increasing connection between systems such as Energy Distribution System, }
  \script<2->{Traffic management, }
  \script<3->{Heat distribution, }
  \script<4->{Water distribution and many others we stroll to the so called smart cities\\}
  \script<5->{The systems are usually }
  \script<5->{Geographically distributed }
  \script<6->{Coupled by constraints as maximum input power or energy }
  \script<7->{and when they are implemented we try to optimize objectives such as cost, energy, user satisfaction and others.\\ }
  \script<8>{A solution is to use Model Predictive Control.}
\end{frame}

\begin{frame}{Model Predictive Control}
  Objective: Find control input sequence that optimizes an objective function
  \only<1-5>{\begin{equation*}
    \begin{matrix}
      \underset{\vec{u}(k:k+\alert<3>{N_{p}}-1|k)}{\mathrm{optimize}}&\alert<2>{J(\vec{x}(k),\vec{u}(k))}\\
      \mathrm{subject~ to}&
      \left.
        \begin{matrix}
          \alert<4>{\vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi))}\\
          \alert<5>{g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0}\\
          \alert<5>{h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0}\\
        \end{matrix}
      \right\}
      \begin{aligned}
        &\forall \xi\in\{1,\dots,\alert<3>{N_{p}}\}\\
        &\forall i\in\{1,\dots,m\}\\
        &\forall j\in\{1,\dots,p\}
      \end{aligned}
    \end{matrix}
  \end{equation*}}%
\only<6->{
  \begin{equation*}
    \begin{matrix}
      \underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&  \sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}\\
      \mathrm{subject~ to}&
      \left.
        \begin{matrix}
          \vec{x}(\xi+1)=f(\vec{x}(\xi),\vec{u}(\xi)) \\
          g_{i}(\vec{x}(\xi),\vec{u}(\xi))\leq0\\
          h_{j}(\vec{x}(\xi),\vec{u}(\xi))=0\\
        \end{matrix}
      \right\}
      \begin{aligned}
        &\forall \xi\in\{1,\dots,N_{p}\}\\
        &\forall i\in\{1,\dots,m\}\\
        &\forall j\in\{1,\dots,p\}
      \end{aligned}
    \end{matrix}
  \end{equation*}
  }%
  \script<1->{The Model based Predictive Control, for those who don't know is a control strategy where the control is computed by solving an optimization problem }
  \script<2->{with cost J. }
  \script<3->{The system's response for the input u is predicted for a period Np, }
  \script<4->{using the model of the system. }
  \script<5->{And we then add the equality and inequality constraints. }
  \script<6->{Usually the optimization problem is to minimize a quadratic objective function.}
\end{frame}

@@

\begin{frame}{Model Predictive Control}
  \small
  \only<1->{Find optimal control sequence}%
  \only<2->{, apply first element}%
  \only<3->{, rinse repeat}%
  \only<4->{ $\to$ Receding Horizon}%

  \begin{figure}
    \centering
    \foreach \i in {1,...,4}{%
      % \includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
      \only<{\i}>{\input{../img/mpcState\i.tex}}%
      \only<{\i}>{\input{../img/mpcControl\i.tex}}%
    }
  \end{figure}
  \script<1->{We find an optimal control sequence }
  \script<2->{We apply only the first element }
  \script<3->{and then we repeat }
\end{frame}

\begin{frame}{Distributed Model Predictive Control}
  \begin{itemize}
    \item<1> Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
    \item<2-> Solution: Divide and Conquer
  \end{itemize}
  \vfill
  \centering
  \begin{minipage}[c]{.45\linewidth}
    \begin{figure}
      \centering
      \only<1>{
        \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
          \node[draw,
          rectangle,
          trapezium stretches,
          align=center,
          fill=supelecRed!10,
          alt=<{3}>{fill=supelecRed!90,text=white},
          minimum width=3.5cm,
          minimum height=4cm
          ] (block1) {MPC};
        \end{tikzpicture}
      }%
      \only<2->{
        \begin{tikzpicture}[font=\small,thick,node distance=.2cm and .5cm,
          mpcSmall/.style={
            rectangle,
            align=center,
            fill=supelecRed!10,
            minimum width=2.cm,
            minimum height=.4cm},
          coordinator/.style={
            rectangle,
            align=center,
            fill=supelecRed!10,
            minimum width=1cm,
            minimum height=4cm
          } ]

@@

        \end{tikzpicture}
      }%
    \end{figure}
  \end{minipage}
  \script<1->{The problem is when the systems are large, since the complexity depends on Np the number of constraints and sizes of input and states }
  \script<2->{The solution is to divide the problem where it is separable and use a coordinator to create a consensus in the coupling variables or constraints}
\end{frame}

\begin{frame}{Distributed Model Predictive Control}{Quantity Decomposition | Resource Allocation}
  \centering
  \only<4->{
    \begin{minipage}[t]{.3\linewidth}
      \begin{figure}[!t]
        \scalebox{.7}{\footnotesize \def\svgwidth{8cm} \input{../img/diagQuantMod.pdf_tex}}
      \end{figure}
    \end{minipage}
    \hfill
  }
  \only<1>{
    \begin{equation*}
      \scalebox{1}{
        $\displaystyle
        \begin{matrix}
          \underset{\vec{u}_i(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\overbrace{\sum\limits^{M}_{i=1} \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}_i(k+j|k)\|^{2}_{Q_i}+\|\vec{u}_i(k+j-1|k)\|^{2}_{R_i}}^{\textstyle J_{i}(k)}}^{\textstyle J_{G}(k)}\\
          \mathrm{subject~ to}&
          \left.
            \begin{matrix}
              \vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
              \sum^{M}_{i=1}\Gamma_{i}\vec{u}_{i}(k)=\vec{u}_{\mathrm{\max}}\\
            \end{matrix}
          \right\}
          \begin{aligned}
            &\forall i\in\{1,\dots,M\}\\
            &\forall j\in\{1,\dots,N_{p}\}
          \end{aligned}
        \end{matrix}
        $}
    \end{equation*}
  }
  \only<2->{
    \begin{minipage}[t]{.6\linewidth}
      \centering
      \begin{equation*}
        \scalebox{.8}{
          $\displaystyle
          \left.
            \small
            \begin{aligned}
              J_{i}^{\star}(\vec{\theta}_{i}(k))&=\underset{\vec{u}_{i}(k:k+N_{p}-1|k)}{\mathrm{minimize}}J_i(k)\\
              \mathrm{s.t.} &\quad\vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
              &\quad\Gamma_{i}\vec{u}_i(k)=\vec{\theta}_{i}(k):\vec{\lambda}_{i}(k)\\
            \end{aligned}
          \right\}
          \small
          \begin{aligned}
            &\forall i\in\{1,\dots,M\}\\
            &\forall j\in\{1,\dots,N_{p}\}
          \end{aligned}
          \label{eq:DOP_local}
          $}
      \end{equation*}
      \vfill
      \begin{equation*}
        \small
        \begin{aligned}
          \only<2>{
            J^{\star}&=\underset{\vec{\theta}(k:k+N_{p}-1|k)}{\mathrm{minimize}}\sum^{M}_{i=1} J^{\star}_i(\vec{\theta}_i(k))\\
            \mathrm{s.t.} &\quad \sum_{i=1}^{M}\vec{\theta}_{i}(k)=\vec{u}_{\max}
          }
          \only<3->{
            \vec{\theta}_{i}\pplusone=\vec{\theta}_{i}\p+\rho\left(\vec{\lambda}_{i}^{\star}(\vec{\theta}_{i}\p)-\frac{1}{M}\sum^{M}_{j=1} \vec{\lambda}_{j}^{\star}(\vec{\theta}_{j}\p)\right)
          }
        \end{aligned}
      \end{equation*}
    \end{minipage}
  }
  \script<1->{An example of decomposition method is the Quantity decomposition where a semi-decomposable problem with a global coupling constraints can be decomposed into }
  \script<2->{multiple sub-problems, which can be solved in parallel, and a master problem which corresponds to the initial problem. \\
   Those coupling constraints are replaced by local constraints with an allocation theta i. }
  \script<3->{The allocation for each sub-problem is updated by a projected subgradient method solving the master problem, thus the original problem. The subgradient used in this method is the dual variable associated to the coupling constraints}
  \script<4->{We can represent the sub-problems as agents and the master problem as a coordinator. The coordinator sends the allocations for each agent, which responds with a dual variable. }
\end{frame}
% \begin{frame}
%   \centering
%   \begin{minipage}{.65\linewidth}
%     \begin{algorithm}[H]
%       \DontPrintSemicolon
%       Coordinator initializes $\vec{\theta}^{(0)}$ \;
%       $p:=0$\;
%       \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
%         Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
%         Coordinator updates allocations~\eqref{eq:thetaNegot}\;
%         $p:=p+1$
%       }
%       \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
%     \end{algorithm}
%   \end{minipage}
% \end{frame}

\begin{frame}{Quantity Decomposition | Resource Allocation}
  \centering
  \begin{minipage}{.45\linewidth}
    \begin{figure}
      \centering
      \scalebox{.55}{
        \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
          \node[draw,
          rounded rectangle,
          fill=gray!90!black!50,
          alt=<{2}>{fill=supelecRed!90,text=white},
          minimum width=2.5cm,
          minimum height=1cm] (block1) {Start};

@@

        \end{tikzpicture}
      }
      % \caption{Quantity decomposition based DMPC}\label{fig:quantityDecompDMPC}
    \end{figure}
  \end{minipage}
  \only<7->{\begin{minipage}{.45\linewidth}
    \begin{figure}
      \centering
      \includegraphics[width=\textwidth]{dmpcQuantity4systemsTriche_.mat_thetalambdanegot.pdf}
    \end{figure}
  \end{minipage}}
  \script<1->{In a flowchart for a quantity decomposition based DMPC,}
  \script<3->{the coordinator sends the allocation theta, }
  \script<4->{the agents send the dual variable lambda, }
  \script<5->{the coordinator updates the allocation. }
  \script<6->{If negotiation converges, }
  \script<7->{then the negotiation ends and each agent applies the first element of the control found}
\end{frame}

\begin{frame}{}
  \centering
  \vfill
What if agents send a non-agreed $\vec{\lambda}_{i}$?
  \vfill
  \script<1>{But what if the agents send a non-agreed lambda?}
\end{frame}

\begin{frame}{Outline}
  % \tableofcontents
  \tableofcontents[subsectionstyle=show/show/show,pausesections]
  % You might wish to add the option [pausesections]
  \script<1->{To respond this this presentation is divided into 3 parts.}
  \script<1->{First We present the vulnerabilites of this decomposition method, }
  \script<2->{We propose one way to secure the method,}
  \script<3->{and finally we present our results.}
\end{frame}

@@

  \begin{itemize}
    \item<1-> $\vec{\lambda}_{i}$ is the only interface with coordination
    \item<2-> Non-cooperative agent sends $\tilde{\vec{\lambda}}_{i}=\gamma_{i}(\vec{\lambda}_{i})$\pause
  \end{itemize}
\script<1->{How can an agent attack the system? Its only interface with the coordination is lambda}
\script<2->{so we suppose it attacks by sending a different $lambda_i$, modified by a function $gamma_i$ of $lambda_i$ }
\end{frame}

\subsection{Consequences}
\begin{frame}{Example}
  \begin{minipage}[c]{.45\linewidth}
    \begin{figure}[!t]
      \centering
      \begin{tikzpicture}
        \node (0,0){\includegraphics[width=\textwidth]{changeOfJ.pdf}};
        \draw<4>[rounded corners,red,thick] (-2.3,2.5) rectangle +(.5,-5);
        \draw<5>[rounded corners,red,thick] (2.3,2.5) rectangle +(.75,-5);
      \end{tikzpicture}
    \end{figure}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{.45\linewidth}
    \begin{exampleblock}{4 distinct agents}
      \begin{itemize}
        \item<2-> Agent 1 is non-cooperative\\
        \item<3-> It uses $\tilde{\vec{\lambda}}_{1}=\gamma_{1}(\vec{\lambda}_{1})=\tau_{1}I\vec{\lambda}_{1}$
      \end{itemize}
    \end{exampleblock}
  \end{minipage}
\script<1->{We give an example of 4 agents negotiating }
\script<2->{Agent 1 is non-cooperative\\ }
\script<3->{It uses a linear cheating function gamma tau times identity times the original lambda i\\ }
\script<3->{In the figure we can see the cost functions for each agent, we see that agent 1 cost decreases if we increase tau, but the overall cost is increased, The minimum value of the global cost is when \\ }
\script<4->{tau is equal to one. If tau is close to zero it increases its cost and if tau is too high\\ }
\script<5->{it can turn the negotiation unstable \\ }
\end{frame}

\section{Securing the DMPC}
\script<1->{In order to secure the method let's analyze the subproblems \\ }

@@

\end{itemize}
\script<1->{Now, for the mitigation the main idea is to reconstruct the original lambda from the estimated parameters and use it in the negotiation\\ }
\script<2->{We suppose the agent wants to decrease its cost, and the lambda sent is only equal to zero if the original is equal to zero. which implies the matrix T is invertible\\ }
\script<3->{We can estimate the inverse of T, by using the estimate of P tilde and the nominal value of P like in this equation\\ }
\script<4->{With the estimate of the inverse of T and the estimate of s tilde, we can reconstruct the original lambda\\ }
\end{frame}

@@

      \node[] at (5cm,0cm) {\Large \alert<2>{Detection Phase}};
      \node[] at (11cm,0cm) {\Large \alert<3>{Negotiation Phase}};

      \node[draw,
      rounded rectangle,
      fill=gray!90!black!50,
      alt=<{4}>{fill=supelecRed!90,text=white},
      minimum width=2.5cm,
      minimum height=1cm] (block1) {Start};
